### 2012-03-15 docs/architecture/architecture.tex
updated directory structure fig
some BC description

\begin{figure}[t]
\centering
\includegraphics[scale=0.65]{\archfigpath/maestro_directory2}
\caption[\maestro\ directory structure]
{The basic \maestro\ directory structure.}
\end{figure}

@@

>>>>

\begin{figure}[]
\centering
\includegraphics[scale=0.55]{\archfigpath/maestro_ecosystem2}
\caption[\maestro\ directory structure]
{The basic \maestro\ directory structure.}
\end{figure}

@@

When \maestro\ is run, the boundary condition parameters are read in
from the input file and used to build the \bctower.  The
\bctower\ consists of a \bclevel\ object for each level of resolution
in the simulation.  The \bclevel\ contains 3 difference descriptions
of the boundary conditions for each box in the domain at that level of
refinement: {\tt phys\_bc\_level\_array}, {\tt
  adv\_bc\_level\_array}, and {\tt ell\_bc\_level\_array}.

Each level has a {\tt phys\_bc\_level\_array(0:ngrids,dim,2)} array,
where {\tt ngrids} is the number of boxes on that level.  This stores
the physical desciption of the boundary type (outlet, inlet, slipwall,
etc.)---this description is independent of the variables that live on
the grid.  The {\tt phys\_bc\_level\_array(0,:,:)} `box' refers to the
entire domain.  If an edge of a box is not on a physical boundary,
then it is set to a default value (typically {\tt INTERIOR}).  
These boundary condition types are used to interpret the actual 
method to fill the ghostcells for each variable, as described in 
{\tt adv\_bc\_level\_array} and {\tt ell\_bc\_level\_array}.

The convention is that the first {\tt dm} variables in the
\bclevel\ refer to the velocity components, and the subsequent slots
are for the other standard variables described in the {\tt
  variables\_module}.  For instance, to reference the boundary
condition for density, one would index with {\tt dm+rho\_comp}.
For temporary variables that are created on the fly in the various
routines in \maestro\ there may not be a variable name in {\tt
  variables\_module} that describes the temporary variable.  In this
case, the special variables {\tt foextrap\_comp} and {\tt
  hoextrap\_comp} (first-order and high-order extrapolation) are used.

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the {\tt setbc} routine,
which is called by {\tt multifab\_physbc}.
